\section{Related Work}

\topheading{Overlay Unicast} A significant body of prior work uses overlay networks to improve the performance and resilience of one-to-one data transfers in the Internet and peer-to-peer networks~\cite{andersen2001resilient, kostic2003bullet, castro2003splitstream}.
In clouds, previous work has also leveraged cloud elasticity to further improve performance~\cite{matos2009clon, jain2022skyplane}.
However, they do not consider multicast, and except Skyplane~\cite{jain2022skyplane}, none consider the monetary cost of replication in the cloud.
%\heading{Skyplane}
Handling multicast is challenging.
For example, while~\cite{jain2022skyplane} can leverage elastic resources, cloud pricing models, and overlay networking for bulk unicast replication in the cloud, its techniques are not directly applicable to the multicast setting.
More specifically, Skyplane's flow-based throughput model results in ambiguous multicast distribution tree solutions as it ignores the identity of data sent along multiple paths.
Furthermore, since Skyplane's optimizer is not designed for multicast, it cannot take advantage of techniques such as leveraging multiple distribution trees to alleviate source bottlenecks. 

\heading{Overlay Multicast}
% \todo{Provide reader with context on systems like Overcast, BDS, SplitStream, Bullet, etc.} 
End-system multicast~\cite{chu2002case} and overlay multicast have been proposed to efficiently disseminate data from a single source to multiple destinations. 
Many application-level multicast algorithms have been proposed. 
%Most of them are based on single or multiple multicast trees per sender. 
Algorithms like SPIDER~\cite{ganguly2005fast}, SplitStream~\cite{castro2003splitstream}, Bullet~\cite{kostic2003bullet}, and Overcast~\cite{jannotti2000overcast} are designed for high-bandwidth, cross-internet file distribution with application-level multicast overlays.
However, 
like with most overlay unicast systems, 
these algorithms ignore monetary costs and focus on techniques to maximize bandwidth. 

 \heading{Inter-DC Replication}
Extensive prior work addresses inter-DC replication~\cite{sima2022ekko, flinn2022owl, zhang2018bds, laoutaris2011inter, feng2012jetway}, including bulk multicast~\cite{luo2019deadline}. Recent research includes deadline~\cite{luo2019deadline} and cost-awareness~\cite{fatemipour2022cost, feng2012jetway}. However, the cost model in the Inter-DC setting cannot be easily adapted to cloud users, for which network pricing is based on total data volume rather than bandwidth.  Furthermore, existing formulations are not designed for multicast~\cite{fatemipour2022cost, feng2012jetway} or do not consider more than a few geo-distributed regions~\cite{luo2019deadline}.  Our work focuses on public clouds, considering unique per-GB network pricing, elastic resources, and cloud-specific resource constraints.  Our approximation algorithm is also designed to scale to all regions across multiple cloud vendors.

 \heading{Traffic Engineering}
The classic problem of traffic engineering has also formulated optimization problems for minimizing cost under performance constraints.
These techniques have recently been applied to cloud providers and their monetary costs.
For example, Entact~\cite{zhang2010optimizing} studied how to optimize costs for online service providers while still minimizing user latency.  
Similarly, Cascara~\cite{singh2021cost} leveraged latency-equivalent paths to identify cost-minimizing paths for cloud providers.
Like Inter-DC Replication, these approaches have been developed from the perspective of the cloud or service provider and, thus, present a materially different optimization problem.


\heading{Steiner Trees}
The Steiner Tree algorithm has been applied in the multicast setting both to minimize costs in terms of delay~\cite{jiang2016constructing} and cloud egress costs~\cite{garcia2015cost}).  CloudMPCast~\cite{garcia2015cost} minimizes egress costs in cloud bulk data multicast by constructing a Steiner Tree overlay network that avoids low-throughput cross-region paths.  However, CloudMPCast overlooks VM capacity and per-VM egress/ingress limits in its MILP formulation.  Also, CloudMPCast aims to achieve \textit{comparable} performance to direct transfers while minimizing cost, unlike \sys, which optimizes throughput. 


\heading{Geo-Distributed Storage}
Geo-distributed storage via data replication is supported by a variety of cloud services, such as AWS Cross-Region Replication~\cite{aws-replication}, AWS Multi-Region Access Points~\cite{aws-access-point}, and GCP Multi-region buckets~\cite{gcp-multi-region-bucket}.  Cross-region replicated buckets (e.g., S3 replication rules) automatically replicate written data from a bucket in one region to one or more buckets in other regions.  However, these services have limited support for cross-cloud data movement and do not minimize egress costs even for intra-cloud data movement.  SPANStore~\cite{wu2013spanstore} designs a system for geo-distributed storage across multiple cloud providers, and also optimizes egress costs of relaying data on PUT requests.  However, its relay strategy is optimized for latency, not bandwidth.  \shu{they actually do consider latency as an SLO constraint, same as ours; the difference is the resource limit constraint}

\heading{Peer-to-peer Multicast}
Peer-to-peer systems (P2P) support file sharing among a set of end-user clients.
% 
The BitTorrent protocol~\cite{cohen2003incentives} reduces the network load on the source by allowing clients to upload and download data to each other. 
% 
BitTorrent is widely used for data multicast in data center environments by Facebook~\cite{facebook-bittorrent} and Twitter~\cite{twitter-bittorrent}.
% 
Specialized systems for data multicast that use BitTorrent include Uber's Kraken~\cite{uber-kraken} and Ant Group's Dragonfly~\cite{dragonfly}.
% 
These P2P systems have significant overhead as they are designed for adversarial settings where peers may be unreliable or fail.
% 
Moreover, P2P systems must scale to millions of destinations and therefore lack centralized control which prevents custom routing topologies.
% 
P2P systems may redundantly send data over expensive links due to a lack of cost awareness. 

\begin{table}[tb]
	\footnotesize
	\begin{center}
        		\resizebox{\columnwidth}{!}{%
		\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
		\begin{tabular}{@{}lccccc@{}}
			\toprule
\textsc{Method}   & \begin{tabular}{@{}c@{}}\textsc{Multicast} \\\end{tabular} & \begin{tabular}{@{}c@{}}\textsc{Cloud} \\ \textsc{Pricing}\end{tabular} & \begin{tabular}{@{}c@{}}\textsc{Striping} \end{tabular} & \begin{tabular}{@{}c@{}}\textsc{Resource} \\ \textsc{Elasticity}\end{tabular} \\
			\midrule
			\multicolumn{5}{@{}l}{\textbf{Unicast overlay networks}} \\
			RON~\cite{andersen2001resilient} & $\times$ & $\times$ & $\checkmark$ & $\times$\\
			Skyplane~\cite{jain2022skyplane} & $\times$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\ 
                COMS~\cite{fatemipour2022cost}& $\times$  & $\times$ & $\times$ & $\sim$\\ 
			\midrule
			\multicolumn{5}{@{}l}{\textbf{Peer-to-peer}} \\
			BitTorrent~\cite{cohen2003incentives} & $\checkmark$ & $\times$ & $\checkmark$ & $\times$\\
			SplitStream~\cite{castro2003splitstream} & $\checkmark$ & $\times$ & $\checkmark$ & $\times$\\
			Bullet~\cite{kostic2003bullet} & $\checkmark$ & $\times$ & $\checkmark$ & $\times$\\
			\midrule
			\multicolumn{5}{@{}l}{\textbf{Inter-DC overlay multicast}} \\
			SPIDER~\cite{ganguly2005fast} & $\checkmark$ & $\times$ & $\checkmark$ & $\times$\\
			%QuickCast & TODO & TODO & TODO & TODO \\
			CodedBulk~\cite{tseng2021codedbulk} & $\checkmark$ & $\times$ & $\checkmark$ & $\times$\\
			BDS~\cite{zhang2018bds} & $\checkmark$ & $\times$ & $\checkmark$ & $\times$\\
                Deadline-aware Inter-DC~\cite{deadline2018} & $\checkmark$ & $\times$ & $\times$ & $\checkmark$ \\
			\midrule
			\multicolumn{5}{@{}l}{\textbf{Cost optimized overlay networks}} \\
			SPANStore~\cite{wu2013spanstore} & $\checkmark$ & $\checkmark$ & $\times$ & $\times$\\
            CloudMPCast~\cite{garcia2015cost} & $\checkmark$ & $\checkmark$ & $\times$ & $\times$\\
            Jetway~\cite{feng2012jetway} & $\times$ & $\checkmark$ & $\checkmark$ & $\times$ \\
            \midrule
			\rowcolor{Gray} \sys (ours) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\ 
			\bottomrule
		\end{tabular}
  }
	\end{center}
	\caption{\sys{} builds on prior work by enabling multicast, optimizing cloud costs, and leveraging cloud resource elasticity and multiple distribution trees.}
	\label{tab:updated_baselines}
\end{table}
